Mass surveillance in cyberspace and the lost art of keeping a secret\thanks{The ideas discussed here first appeared as a DCSS project conference talk and were subsequently fleshed out in paper due to serendipitous encounters fostered by twitter.}

### 2015-07-08 paper.tex
Ack

\title{Mass surveillance in cyberspace and the lost art of keeping a secret\thanks{Ideas discussed here first appeared as a DCSS project conference talk and were then fleshed out as paper due to the serendipitous nature of encounters fostered by twitter.}}
\subtitle{Policy lessons for nation-states after the Snowden leaks}

>>>>

\title{Mass surveillance in cyberspace and the lost art of keeping a secret\thanks{The ideas discussed here first appeared as a DCSS project conference talk and were subsequently fleshed out in paper due to serendipitous encounters fostered by twitter.}}
\subtitle{Policy lessons for nation-states after the Snowden leaks}
